Preferences interact: what consequences for a Schelling scenario?

### 2019-11-08 ethnic_value_rum.Rmd
setup and ref

* Schelling's model and previous work. Interaction of preferences.
Schelling's model
Literature update
@paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018

* Update: justification for random utility models
Better define the individual  decision process
Link with empirical data

>>>>

* Schelling's model and previous work. Interaction of preferences.
Schelling's model
Literature update
@paolillo2018 Diverse dimensions can define individuals and their similarity. Results from @paolillo2018
@hedstrom2009oxford, chapter 11, 12

* Why an additional characteristic than ethnicity, literature in residential studies

* Update: justification for random utility models, literature in ABM
Better define the individual  decision process
Link with empirical data
@huang2014review
@klabunde2016decision
@bruch2019choice
